Microlensing as a possible probe of event-horizon structure in quasars

### 2016-03-14 paper1/ms.tex
Changes

\textit{Author contributions}\\
Prasenjit Saha provided the original idea and plan for the research project as well as multiple contributions to the analysis.
 Mihai Tomozeiu simulated and studied the ideal behaviour of the microlensing lightcurves for the different source profiles discussed.
 Joachim Wambsganss provided the numerical code used by Manuel Rabold to create the magnification map and corresponding lighcurves 
used in the MCMC analysis performed by Irshad Mohammed in the last part of the presented work.

>>>>

\textit{Author contributions}\\
Prasenjit Saha provided the original idea and plan for the research project as well as multiple contributions to the analysis and manuscript preparation. Mihai Tomozeiu simulated and studied the ideal behaviour of the microlensing lightcurves for the different source profiles discussed and prepared the manuscript.
 Joachim Wambsganss provided the numerical code used by Manuel Rabold to create the magnification map and corresponding lighcurves 
used in the MCMC analysis performed by Irshad Mohammed in the last part of the presented work. Both Manuel Rabold and Irshad Mohammed had large contributions in writting the "Fitting Mock Data" section.
